Argennon: A Scalable Smart Contract Platform

### 2022-04-22 tex/A.tex
Fix some readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

        The Argennon network relies on a permission-less network of Publicly Verifiable Database (PV-DB) servers,
        which forms the Argennon cloud. A PV-DB server is a conventional data server which uses its computational and
        storage resources to help the Argennon network process transactions. A large portion of incentive rewards in
        the Argennon platform is devoted to PV-DB servers. This will incentivize the development of conventional
        networking, storage and computational hardware, which can benefit all areas of information technology.
    \end{abstract}
    \tableofcontents

>>>>

        The Argennon cloud is formed by a permission-less network of Publicly Verifiable Database (PV-DB) servers. A
        PV-DB server in Argennon, is a conventional data server which uses its computational and
        storage resources to help the Argennon network process transactions. A large portion of incentive rewards in
        the Argennon platform is devoted to PV-DB servers. This incentivizes the development of conventional
        networking, storage and computational hardware, which can benefit all areas of information technology.
    \end{abstract}
    \tableofcontents

### 2022-04-22 tex/sections/avm.tex
Fix some readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

An Argennon Standard Representation (ASR) is a programming language for describing argennon applications, optimized
for the architecture and requirements of the Argennon platform.
Argennon supports two standard representations: one is a high level text based language which needs
costly compilation before being executed on a hardware machine. The other is a low level binary representation which
usually can be executed, with minimal pre-processing, by a JIT compiler or an emulator. The high level
language is intended for preserving the high level information of applications logic to facilitate
platform specific compiler optimization at host nodes. The low level language, on the oder hand, is designed for
efficient direct execution of applications that are not frequently used.

@@

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data for executing requests are retrieved from the Argennon cloud and the helper data structures are constructed.
This step is
designed in a way that can be done fully in parallel for each request without any risks of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution dag} data
structure and in the final step, requests are executed using that data structure.

@@

Resource usage can be measured per session or per application call. Obviously per session measurement is
easier and more efficient. However, when we measure resources per session if
a session violates its resource caps, determining the point of failure may require precise and error-free resource
measurement. Note that for implementing optional decoupling principle in Argennon, we need to determine the exact
application call which has failed in a call chain. For example, assume that a session containing an application call
violates a 2 milliseconds execution time cap. If in the caller's code, the call happens exactly after 2 milliseconds,
a small fluctuation in the execution time measurement can
change the point of failure between the called and the caller application. This can introduce nondeterministic
behaviour which could make block validation impossible. That's why the AscEE sometimes uses per application call
resource management. If we define the resource caps per application call and perform our measurements for each
application call separately, by using caps that are larger than the measurement error, errors in the
measurements would not change the point of failure in the call chain.

@@

If a proposed block contains many transactions which need a lot of run-time resources, validators would not
be able to validate all transactions in a timely manner. Consequently, they may decide to reject the block or if they
spend enough resources, the confirmation of that block could take more time than usual. Longer block time is not
favoured by block proposers, because it means less throughput of the system which usually means less overall rewards
for them. In Argennon the management of run-time resources, is left to the block proposer.

@@

In Argennon, execution time and local memory are considered \emph{nondeterministic} resources. A nondeterministic
resource is a resource that can not be measured precisely and its measurement always contains a random error.
Optimistic sessions are not allowed to fail because of violating nondeterministic resource limits. As a result, the
block proposer must always choose a monitored session for a transaction that violates a nondeterministic resource cap
and is included in his block.

When a transaction fails due to violation of a limit for a nondeterministic resource, the proposer is
required to exactly specify the application call in the session that violates that limit. When validators are
executing a monitored session, for each application call, they enforce considerably larger limits for
nondeterministic resources, only when the proposer has declared that an application call violates a limit the
validators will enforce the actual value of the limit. This simple mechanism ensures that, with a very high
probability, validators agree with the proposer.

>>>>

An Argennon Standard Representation (ASR) is a programming language for describing argennon applications, optimized
for the architecture and requirements of the Argennon platform.
Argennon supports two standard representations. One representation is a high level text based language which needs
costly compilation before being executed on a hardware machine. The other, is a low level binary representation which
usually can be executed, with minimal pre-processing, by a JIT compiler or an emulator. The high level
language is intended for preserving the high level information of applications logic to facilitate
platform specific compiler optimization at host nodes. The low level language, on the oder hand, is designed for
efficient direct execution of applications that are not frequently used.

@@

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data for executing requests are retrieved from the Argennon cloud and the helper data structures are constructed.
This step is
designed in a way that can be done fully in parallel for each request without any risk of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution dag} data
structure and in the final step, requests are executed using that data structure.

@@

Resource usage can be measured per session or per application call. Obviously per session measurement is
easier and more efficient. However, when we measure resources per session if
a session violates its resource caps, determining the point of failure may require precise and error-free resource
measurement. For example, assume that a session containing an application call
violates a 2 milliseconds execution time cap. If in the caller's code, the call happens exactly after 2 milliseconds,
a small fluctuation in the execution time measurement can
change the point of failure between the called and the caller application. Note that for implementing optional
decoupling principle in Argennon, we need to determine the
exact application call which has failed in a call chain, and this fluctuation introduces a nondeterministic
behaviour which could make block validation impossible. That's why the AscEE sometimes uses per application call
resource management. If we define the resource caps per application call and
perform our measurements for each application call separately, by using caps that are larger than the measurement
error, errors in the measurements would not change the point of failure in the call chain.

@@

If a proposed block contains many transactions which need a lot of run-time resources, validators would not
be able to validate all transactions in a timely manner. Consequently, they may decide to reject the block or if they
spend enough resources, the confirmation of that block could take more than usual time. Longer block time is not
favoured by block proposers, because it means less throughput of the system which usually means less overall rewards
for them. In the Argennon protocol the management of run-time resources, is left to the block proposer.

@@

In Argennon, execution time and local memory are considered \emph{nondeterministic} resources. A nondeterministic
resource is a resource that can not be measured precisely and its measurement always contains a random error.
Optimistic sessions are not allowed to fail because of violating nondeterministic resource limits. As a result, the
block proposer must always choose a monitored session for a transaction that is included in his block and violates a
nondeterministic resource cap.

When a transaction fails due to violation of a limit for a nondeterministic resource, the proposer is
required to exactly specify the application call in the session that violates that limit. When validators are
executing a monitored session, for each application call, they enforce considerably larger limits for
nondeterministic resources, only when the proposer has declared that an application call violates a limit, the
validators will enforce the actual value of the limit. This simple mechanism ensures that, with a very high
probability, validators agree with the proposer.
